### Project Info
---
title: "R-eproducibility"
author: "mstewart2000"
date: "26/01/2022"
output: html_document
GitHub Link: https://github.com/mstewart2000/R-eproducibility/tree/main
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initial Setup
# Loading packages and setting up working directory
```{r echo = FALSE}
library(dplyr)
library(readr)
getwd()
```

# Load data from folder and check integrity
```{r}
head(data) 
str(data)
```

## Reorganize Data
# Remove rows with Biomass > 60
```{r}
data = data %>%
  filter(Total < 60)
```

# Rearrange Collums and only keep Total, Taxon, Scenario, and Nutrients
```{r}
data = data %>%
  select(Total, Taxon, Scenario, Nutrients) %>%
  arrange(Total, Taxon, Scenario, Nutrients)
```

# Create a new collum which is Total Biomass in Grams
```{r}
data = data %>%
  mutate(TotalG = Total/1000) %>%
  select(TotalG, Taxon, Scenario, Nutrients)
```

## Custom Function
# This function will allow you to find the average, sum, or number of observations for a selected column
# Please follow the following input method -> (data.frame$column.name, "argument")
# Possible arguments are: Average, Sum, Observations
```{r}
DataInformation <- function(x, y) {
  t <- if (y == "Average") {
    print(paste("The average of the selected column is:", mean(x)))
  } else if (y == "Sum") {
    print(paste("The sum of the selected column is:", sum(x)))
  } else if (y == "Observations") {
    print(paste("The length of the selected column is:", length(x)))
  } else {
    print(paste("Error: please ensure that the selected column exists and that you have chosen either Average, Sum, or Observations"))
  }
}
```

# Testing the Function
```{r}
DataInformation(data$Taxon, "Observations")

DataInformation(subset(data$TotalG, data$Nutrients == "high"), "Average"); DataInformation(subset(data$TotalG, data$Nutrients == "low"), "Average") 
```


## Knitting the Data to the Ouput File
```{r}
write.csv(data, "Output/WrangledData.csv")
```

